Analyzing Build Logs Using Programming by Example

### 2019-06-24 paper/paper.tex
small improvements: ruby tool output & end after number of trys no buildlogs with rare states, timing of learning in c# tool, black headings in paper draft, worklog update 17.6.
output of c# tool in explanation file, try docs folder for publishing, annibales feedback bullet points into paper

\section{Introduction}
\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow}

\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to recover the relevant information from between many uninteresting other lines.

One way to support them would be to extract the desired information and present it in a structured way.
Usually such functionality is realized by tools that employ handcrafted regular expressions to find the desired text parts within the build log.
However, creating these regular expressions is tedious and mentally complicated task, especially when they have to be maintained some months in the future \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.

@@

Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at google. In addition most failures are resolved within two builds. Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones. They determined that testing failures outweigh compilation errors. Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects. Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds. They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.

@@

\draft{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by removing irrelevant terms and stop words, stemming and weighting the remaining words before comparing the similar of those weights against other text parts.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.

In our work we focus on a more precise form of information extraction where we try to obtain a specific detail from a build log instead of retrieving the general idea of a document part.}

@@

\subsubsection{Design}
\bp{
realistic image (for open source software) we sample from popular GitHub repositories that also use Travis CI.

@@

\subsubsection{Execution}
\bp{
built tool X \todo{data collection tool name, LogCollector?}

@@

\subsubsection{Capabilities}

@@

\subsubsection{Limitations}

@@

\subsubsection{Extraction Accuracy}

@@

\subsubsection{Compare to Traditional Methods}
\paragraph{TravisTorrent}
\bp{Beller et al. \mention{cite correct travistorrent paper} reported on manually constructing a parser with regular expressions for ruby \& Java and common build tools / output formats there, they can extract \todo{<explain there extractions, with example necessary?}

@@

\paragraph{Manual Regex Construction}
\plan{
for something where I did not look at the synthesized program

@@

\paragraph{IR paragraph stuff}
\plan{
maybe simple setup with lines implementing vector comparison on keywords ourselves -> how can we reuse the labeling for the c\# tool?
}

\paragraph{Keyword search}
\plan{
either: we give a list of keywords generally associated with the thing we want to extract (e.g. failure/error/..) -> write nicely how we brainstormed that

>>>>

\section{Introduction}
\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow

problem, done in literature, why not eough? our approach
}

\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.

\plan{why are logs so difficult: mention heterogenous, semi-structured (paper reference for that?), big data (refercene paper about log sizes), in distributed systems probably distributed (really also for buildlog?)

to combat that useres write tools to <extract / rerieve superbegriff> information from buildlogs.

one possibility IR: classfy specifict part of program as similar to others (list IR technique) to see whether it is correclated to a failure. but not as good: not a real summarization technique, more what is similar to the last few times it faied.

way to extract fine grained information: regular expressions which have to be written manually

MAYBE IN THE other paragraph. here only half fitting?
}

During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to retrieve the relevant information from between many uninteresting other lines.

One way to support them would be to extract the desired information and present it in a structured way.
Usually such functionality is realized by tools that employ handcrafted regular expressions to find the desired text parts within the build log.
However, creating these regular expressions is tedious, mentally complicated and usually error-prone task. Especially when they have to be maintained for long \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.

@@

Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google. In addition most failures are resolved within two builds. Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones. They determined that testing failures outweigh compilation errors. Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects. Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds. They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.

@@

\draft{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of recieving a paragraph which is similar to a givien query, our works focus more on obtaining specific pieces of texts through regular expressions.

@@

\subsubsection{Design} ...
\bp{
realistic image (for open source software) we sample from popular GitHub repositories that also use Travis CI.

@@

\subsubsection{Execution} ...
\bp{
built tool X \todo{data collection tool name, LogCollector?}

@@

\subsubsection{Capabilities} ...

@@

\subsubsection{Limitations} ...

@@

\subsubsection{Extraction Accuracy}
...

@@

\subsubsection{Compare to Traditional Methods}
\paragraph{TravisTorrent} ...
\bp{Beller et al. \mention{cite correct travistorrent paper} reported on manually constructing a parser with regular expressions for ruby \& Java and common build tools / output formats there, they can extract \todo{<explain there extractions, with example necessary?}

@@

\paragraph{Manual Regex Construction} ...
\plan{
for something where I did not look at the synthesized program

@@

\paragraph{IR paragraph stuff} ...
\plan{
maybe simple setup with lines implementing vector comparison on keywords ourselves -> how can we reuse the labeling for the c\# tool?
}

\paragraph{Keyword search} ...
\plan{
either: we give a list of keywords generally associated with the thing we want to extract (e.g. failure/error/..) -> write nicely how we brainstormed that
